\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2016
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2016}

% \usepackage{nips_2016}

% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage[final]{nips_2016}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{enumitem}
\usepackage{xfrac}

\title{Your Awesome Project Title}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
  Name 1\\
  Department 1\\
  \texttt{id1@andrew.cmu.edu} \\
  \And
  Name 2 \\
  Department 2\\
  \texttt{id2@andrew.cmu.edu} \\
  \And
  Name 3\\
  Department 3\\
  \texttt{id3@andrew.cmu.edu} \\
}

\begin{document}

\maketitle

% \begin{abstract}
% No abstract.
% \end{abstract}

\section*{Instructions}

Your midway report should be 4 pages long (excluding references) and include the following:

\begin{itemize}[leftmargin=2em]
    \item Project title and list of group members (please follow the given template).

    \item \textbf{Introduction (1 -- 1\sfrac{1}{2} pages):}
    Problem and literature overview; how your idea fits into the existing work.
    If you already had an elaborate proposal, you may borrow this part from there, but try to make it as focused and concise as possible.
    If your proposal did not include enough background information, please make sure this section fills that gap (this will also save you time on preparing the final report).

    \item \textbf{Methods (1\sfrac{1}{2} -- 2 pages):}
    If you are developing a new method / model / architecture, this section should contain all the math, derivations, formal details, illustrations (if necessary).
    If you are proving theorems, assumptions and theorem formulations should be here.
    If your project is application driven, this section should highlight important aspects of the application and details on how your methodology addresses those.

    \item \textbf{Preliminary Results (\sfrac{1}{2} -- 1 page):}
    Please include experimental results you have obtained by the deadline.
    We expect you to have at least implemented and tested a major part of your models (maybe on some toy data) and run a few baselines.
    Describe how the current results align with your expectations.
    You may include the details on how you mined / prepared the data, if it is an important aspect of the project.

    \item \textbf{Final plan (\sfrac{1}{2} page):}
    The adjusted plan for the next steps (in terms of methodology, experiments, data collection, etc.)
\end{itemize}

\section*{Additional notes}

If you have changed or adjusted your project plan significantly (compared to what you have proposed), please provide a brief note on this in a subsection of the introduction.

\section*{Grading rubric}

\textbf{Total weight:} 25\% of the project grade (i.e., 10\% of the course grade).

\begin{itemize}[leftmargin=2em]
    \item Introduction \& literature survey (10\%)
    \item Methods (40\%)
    \item Preliminary results (20\%)
    \item Plan of the next steps (20\%)
    \item Quality of writing (10\%)
\end{itemize}

% \subsection*{References}

\end{document}
