\section*{Instructions}

Your final report should be 8 pages long (excluding references) and include the following:

\begin{itemize}[leftmargin=2em]
    \item Project title and list of group members (please follow the given template).

    \item \textbf{Introduction (1--2 pages):}
    Problem statement and literature overview; how your idea fits into the existing work.
    If you already had an elaborate proposal/midway report, you may borrow this part from there, but try to make it focused and concise.
    \emph{If you changed the topic of your project, make sure your introduction matches the problem you study.}


    \item \textbf{Methods (2--4 pages):}
    If you are developing a new method / model / architecture, this section should contain all the math, derivations, formal details, illustrations, etc.
    If you are proving theorems, assumptions, theorem formulations and proofs should be here.
    \emph{Even if your project is purely application driven, methods should include enough details about the models you are using to make your reports self-contained.}

    \item \textbf{Results (2--4 pages):}
    Your experimental results and discussion of thereof.
    Describe how the current results in each of the experiments align with your expectations.
    You may include the details on how you mined / prepared the data, if it is an important aspect of the project.

    \item \textbf{Discussion (\sfrac{1}{2}--1 page):}
    Please discuss the results of your project, including:
    \begin{itemize}
        \item Reiterate the main achievements of your project (proved theorems, interesting results, insights about the problem you were working on, etc.).
        \item Highlight a few limitations of your approach (e.g., strong assumptions you had to make, constraints, when your method didn't work in practice, etc.). Comment on whether you think there is a way to further improve your method to eliminate these limitations.
    \end{itemize}
\end{itemize}

\section*{Additional notes}

Please make sure you address the comments on your midway reports (especially if they specific actions/details are requested).

\section*{Grading rubric}

\textbf{Total weight:} 75\% of the project grade (i.e., 30\% of the course grade).

\begin{itemize}[leftmargin=2em]
    \item Introduction \& literature survey (10\%)
    \item Methods (30\%)
    \item Results (35\%)
    \item Discussion (15\%)
    \item Quality of writing (10\%)
\end{itemize}